Understanding Voter Preferences: A Gender and Education Analysis of the 2022 United States Election

### 2024-03-17 paper/datasheet.qmd

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    -- The Cooperative Election Study made the dataset was created to analyze the number of U.S. adult citizens who vote in U.S. elections and whether their background affects the probability of voting. Select each state as a sample, and then select matches from the middle for further investigation. In this way, the data obtained by combining multiple variables will be more accurate.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The Cooperative Election Study build this dataset and it was made of 60 groups.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The 2022 Cooperative Election Study was supported by the National Science Foundation Award # 2148907. 
4. *Any other comments?*
    - The data given by CES is general, and new data needs to be combined to form a more accurate result.

@@

	- The CES 2022 data represents the electoral behavior of voters when they cast their ballots for candidates, with examples showing that voters' choice lines differ by gender and education.

@@

	- CES has 60,000 cases. It divided the samples of these cases themselves into different variables, which he then screened and cleaned.

@@

	- The dataset does not include all instances, the data is too large, so the CES calculation uses each state to collect data. Voter status is also restricted, for example, to choosing respondents only among adult U.S. citizens. Each state's calculations are better at collecting local data and matching it. A lot of voter data may be lost, the data will not be matched, so the instance will not be able to match other samples.

@@

	- Instance included voter information, political party, election status, equipment participating in the election. These are all variables derived from CES raw data.

@@

	- Yes. For example, in the CES gender's label, his label is gender4.

@@

	- CES only records the data and does not show the corresponding trend, it is easy to analyze a single variable and cannot be combined togethe

@@

	- CES does not give relationships between individual instances, they are more like separate categories and then show data, for example, gender4 in only gender differentiation without adding people and other variables.

@@

	- No.

@@

	- The data recorded by the respondents was lost and could not be matched to the data in the next part of the sample.

@@

	- CES data was collected from individuals on the web or through YouGov's 1000 data survey. The data is kept at the Harvard Dataverse, where it is accessible to all.

@@

	- CES did not have data that could be classified as confidential because it did not involve excessive privacy exposure, and he asked respondents more about their status at the time of the election.

@@

	- Data sets about gender issues and sexual orientation may offend respondents.

@@

	- There are a lot of sub-populations in the data. For example, based on gender, there will not be a single gender, but a variety of genders for respondents to choose from. Secondly, there are 5 education levels. In terms of age, most of the respondents were adults, so the lowest age was from 18 and then all the way up to 65 and over.

@@

	- No, he did not specify a particular person, the data is more to gather each person's data into different categories.

@@

	- Dataset Indicates sensitive data. The Dataset covers race, ethnic origin, religious beliefs, political views, party affiliation, sexual orientation, health data, and crime.

>>>>

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to enable analysis of Australian politicians. We were unable to find a publicly available dataset in a structured format that had the biographical and political information on Australian politicians that was needed for modelling.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - TBD
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - TBD
4. *Any other comments?*
    - TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

### 2024-03-17 paper/paper.qmd

---
title: "Understanding Voter Preferences: A Gender and Education Analysis of the 2022 United States Election"
author: "Bernice(Yixuan) Bao, Zheng(Zeb) Yang, Dongli Sun"
thanks: "Code and data are available at: <https://github.com/iloveyz12/US-Political-Support>. Datasheet is inside the 'paper' folder."
date: "March 11, 2024"
date-format: long
abstract: "This paper investigates and studies the voter turnout of the 2022 the United Status election, and uses the CES research to sample the data and analyze the different groups. We used Bernoulli distribution to explore whether the gender and education of voters have an impact on candidates. We noticed that the analysis found that the majority of the group voted for Biden compared to Trump. Regardless of the level of education and gender differences, Biden's votes basically beat Trump's. Then, we’re going to take a closer study in this phenomenon and we're going to explore why the majority of voters chose Biden. We need the outcome to determine whether they will affect future elections and adjust them."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Understanding Voter Preferences: A Gender and Education Analysis of the 2022 United States Election"
author: "Bernice(Yixuan) Bao, Zheng(Zeb) Yang, Dongli Sun"
thanks: "Code and data are available at: <https://github.com/iloveyz12/US-Political-Support>."
date: "March 11, 2024"
date-format: long
abstract: "This paper investigates and studies the voter turnout of the 2022 the United Status election, and uses the CES research to sample the data and analyze the different groups. We used Bernoulli distribution to explore whether the gender and education of voters have an impact on candidates. We noticed that the analysis found that the majority of the group voted for Biden compared to Trump. Regardless of the level of education and gender differences, Biden's votes basically beat Trump's. Then, we’re going to take a closer study in this phenomenon and we're going to explore why the majority of voters chose Biden. We need the outcome to determine whether they will affect future elections and adjust them."
format: pdf
number-sections: true
bibliography: references.bib
---
